\section{February 2016}
\subsection{\date{2/01/2016}}
\begin{itemize}
\item Applied AV definitions PCs in L-2.\space \Keyboard \space \ComputerMouse  
\item Updated Microsoft Office with patches.
\item Applied patches to Windows.
\end{itemize}

\subsection{\date{2/02/2016}}
\begin{itemize}
\item Applied patches to PCs in L-2.\space \Keyboard \space \ComputerMouse  
\item Captured hard information from JatLand Computers and Servers
\item
\end{itemize}

\subsection{\date{2/03/2016}}
\begin{itemize}
\item JatLand computer spreadsheet. 
\item Drivers for M4800
\item L-1 PC patches
\item L-1 Office patches
\item L-1 AV definitions update
\end{itemize}

\subsection{\date{2/04/2016}}
\begin{itemize} 
\item Imaged M4500 for Marvin Orr \space \Keyboard \space \ComputerMouse
\item Downloaded drivers for an HP
\item Downloaded Office 2013 Service Pack 1 x86 and x64
\item Updated PC with Walter.
\end{itemize}

\subsection{\date{2/05/2016}}
\begin{itemize} 
\item Ran Windows Updates for Mobile Orange
\item External hard drive for Rajani Bhat
\item ePO AD Sync research 
%Was right about needing LDAP setup
\item 
\end{itemize}

\subsection{\date{2/08/2016}}
\begin{itemize} 
\item AoA images
\item Scanfront 300 research
\item Created PDF versions of documentation.
\item 
\end{itemize}

\subsection{\date{2/09/2016}}
\begin{itemize} 
\item Tested Scanfront 300 and it's operational.
\item L-2 ZOG updating
\item ePO 5.3 research
\item L-2 AD corrupt profiles
\end{itemize}

\subsection{\date{2/10/2016}}
\begin{itemize} 
\item Research GPO restrictions and Service Accounts (ePO related)
\item SQL services unable to find image file and run
\item L-2 AD1 corruption. Possible rebuild.
\item 
\end{itemize}

\subsection{\date{2/11/2016}}
\begin{itemize} 
\item Updating Cyclone PCs
\item Zbook for Zach Warren
\item SQL service research
\item 
\end{itemize}

\subsection{\date{2/12/2016}}
\begin{itemize} 
\item Prepared M4500s for removal. 
\item Updating Cyclone PCs
\item Zbook for Zach Warren
\item Departed around 3 o'clock for home repairs
\end{itemize}

\subsection{\date{2/15/2016}}
\begin{itemize} 
\item Updated Cyclone PCs
\item Zbook for Zach Warren
\item 4800 for Justin Allen
\item 
\end{itemize}

\subsection{\date{2/16/2016}}
\begin{itemize} 
\item Re-arm Office Suite for Zach Warren and Justin Allen
\item Adding VS PRO 2015 to CATS machines
\item Updating CATS machines with WSUS
\item 
\end{itemize}

\subsection{\date{2/17/2016}}
\begin{itemize} 
\item Updating CATS machines with WSUS
\item Correct ZJ38 for April Yager
\item Checked-in new DAT file for ePO
\item 
\end{itemize}

\subsection{\date{2/18/2016}}
\begin{itemize} 
\item CATS machine MBR error after Acronis True Image
\item Creating CDS3 baseline on E643
\item Departed early for doctor's appointment
\item 
\end{itemize}

\subsection{\date{2/19/2016}}
\begin{itemize} 
\item Captured M4800, ZJ36 images
\item Attempting to disable USB storage devices.
\item Constructing Shavlik test network for disconnected environment.
\item 
\end{itemize}

\subsection{\date{2/22/2016}}
\begin{itemize} 
\item Constructing Shavlik test network for disconnected environment.
\item Attempting to disable USB storage devices
\item Building Windows baseline images.
\end{itemize}

\subsection{\date{2/23/2016}}
\begin{itemize} 
\item Testing Shavlik
\item Building Windows baseline images.
\item 
\item 
\end{itemize}

\subsection{\date{2/24/2016}}
\begin{itemize} 
\item Testing Shavlik
\item Building Windows baseline images.
\item 
\item 
\end{itemize}

\subsection{\date{2/25/2016}}
\begin{itemize} 
\item Out of the office for a funeral. %Uncle Jerry Studdard
\item 
\item 
\item 
\end{itemize}

\subsection{\date{2/26/2016}}
\begin{itemize} 
\item Captured hard drive info for new laptops going in L-2.
\item Placed remaining laptops in cage. 
\item Informed of becoming Walter's backup for L-1.
\item Informed of taking over managing RedHat licenses.
\end{itemize}

\subsection{\date{2/29/2016}}
\begin{itemize} 
\item Researching RedHat License Management.
\item Assisted Walter in adding laptops to L-2.
\item 
\item 
\end{itemize}
