\newpage
\section{March 2016}
\begin{multicols}{2}
\subsection{\date{3/01/2016}}
\begin{itemize} 
\item Changed physical name of PCs for L-2.
\item Imaged new PCs for L-2.
\item Ran cable for new switches. 
\item 
\end{itemize}

\subsection{\date{3/02/2016}}
\begin{itemize} 
\item Acronis Linux issues.
\item 
\item 
\item 
\end{itemize}

\subsection{\date{3/03/2016}}
\begin{itemize} 
\item Building baseline images.
\item 
\item 
\item 
\end{itemize}

\subsection{\date{3/04/2016}}
\begin{itemize} 
\item Building baseline images.
\item Shavlik Disconnected mode testing.
\item 
\item 
\end{itemize}

\subsection{\date{3/07/2016}}
\begin{itemize} 
\item Shavlik disconnected console
\item Re-image Coft PC with OEM and update.
\item 
\item 
\end{itemize}

\subsection{\date{3/08/2016}}
\begin{itemize} 
\item Shavlik disconnected console
\item Re-image Coft PC with OEM and update.
\item Shavlik documentation.
\item 
\end{itemize}

\subsection{\date{3/09/2016}}
\begin{itemize} 
\item Build Coft image from OEM disk.
\item 
\item 
\item 
\end{itemize}

\subsection{\date{3/10/2016}}
\begin{itemize} 
\item Build Coft image from OEM disk.
\item 
\item 
\item 
\end{itemize}

\subsection{\date{3/11/2016}}
\begin{itemize} 
\item Privileged User Account training course
\item Coft PC image build
\item 
\item 
\end{itemize}

\subsection{\date{3/14/2016}}
\begin{itemize} 
\item Red Hat rebuild with EXT4 file system instead of LVM with Terry Ledford
\item 
\item 
\item 
\end{itemize}

\subsection{\date{3/15/2016}}
\begin{itemize} 
\item Re-image Coft PC with AGM
\item Prepare 2 ZBooks for Coft use
\item Red Hat and Acronis True Image 2014 deployment issues
\item Deploy Red Hat ZBook to Rick Hinkelmann
\end{itemize}

\subsection{\date{3/16/2016}}
\begin{itemize} 
\item Red Hat deployment discovery 
\item Deploy 2 ZBooks CDS3 to Marvin Orr.
\item S.A.T.S. first look demo
\item 
\end{itemize}

\subsection{\date{3/17/2016}}
\begin{itemize} 
\item Building baseline images
\item Red Hat McAfee Agent install
\item CDS3 Zbook for Marvin had to be re-imaged.
\item 
\end{itemize}

\subsection{\date{3/18/2016}}
\begin{itemize} 
\item Baseline images
\item JATDev Zbook with NetBeans installed on C:
\item 
\item 
\end{itemize}

\subsection{\date{3/21/2016}}
\begin{itemize} 
\item Red Hat McAfee ePO GUI
\item 2 ZBooks for Quantitech
\item JATDev Zbook ACAS scan
\item 
\end{itemize}

\subsection{\date{3/22/2016}}
\begin{itemize} 
\item 2 ZBooks for Quantitech
\item JATDev Zbook capture
\item JATDev Zbook for Greg Brock.
\item Updating Cowboy image
\end{itemize}

\subsection{\date{3/23/2016}}
\begin{itemize} 
\item Updated Developer Image
\item Updated Cowboy Image
\item Preparing 13 JAT Developer ZBooks
\item 
\end{itemize}

\subsection{\date{3/24/2016}}
\begin{itemize} 
\item Preparing 13 JAT Developer ZBooks
\item Acronis Red Hat Deployment
\item 
\item 
\end{itemize}

\subsection{\date{3/25/2016}}
\begin{itemize} 
\item Acronis Red Hat Deployment
\item
\item 
\item 
\end{itemize}

\subsection{\date{3/28/2016}}
\begin{itemize} 
\item Acronis Red Hat Deployment
\item Deploying JAT Developer ZBooks
\item ZBook for Kristina Beonker
\item 
\end{itemize}

\subsection{\date{3/29/2016}}
\begin{itemize} 
\item JAT Developer enable USB
\item CDS3 ethernet dongle testing
\item 
\item 
\end{itemize}

\subsection{\date{3/30/2016}}
\begin{itemize} 
\item CDS3 ethernet dongle testing
\item L-2 CD-ROM repair
\item L-2 Monthly software updates
\item L-1 Monthly software updates
\end{itemize}

\subsection{\date{3/31/2016}}
\begin{itemize} 
\item L-1 Monthly software updates
\item Developed Red Hat Offline update procedure with Walter Rogers and Andy Eadon
\item 
\item 
\end{itemize}
\end{multicols}