\newpage
\section{April 2016}
\begin{multicols}{2}
\subsection{\date{4/01/2016}}
\begin{itemize} 
\item CAC application
\item 
\item Left early due to illness
\item 
\end{itemize}

\subsection{\date{4/04/2016}}
\begin{itemize} 
\item Challenges 2016 Q1 documentation
\item Red Hat Offline Updates Repository documentation
\item 
\item 
\end{itemize}

\subsection{\date{4/05/2016}}
\begin{itemize} 
\item CDS3 USB to Ethernet dongle testing. Haven't reproduce errors
\item L2 Adobe and Cygwin install
\item 
\item 
\end{itemize}

\subsection{\date{4/06/2016}}
\begin{itemize} 
\item CDS3 USB to Ethernet dongle testing.
\item CAC retrieval 
\item 
\item 
\end{itemize}

\subsection{\date{4/07/2016}}
\begin{itemize} 
\item CDS3 USB to Ethernet dongle testing
\item Setup PTS WSUS and ACAS network
\item RedHat VirtualBox imaging
\item Notes on NISPOM
\end{itemize}

\subsection{\date{4/08/2016}}
\begin{itemize} 
\item Creating image from scratch for Other Contractors
\item RedHat VirtualBox imaging
\item 
\item 
\end{itemize}

\subsection{\date{4/11/2016}}
\begin{itemize} 
\item Creating image from scratch for Other Contractors
\item RedHat VirtualBox imaging
\item 
\item 
\end{itemize}

\subsection{\date{4/12/2016}}
\begin{itemize} 
\item Imaged 5 ZBooks for Raytheon and 2 ZBooks for Lockheed
\item CentOS 5 offline update method
\item 
\item 
\end{itemize}

\subsection{\date{4/13/2016}}
\begin{itemize} 
\item CentOS 5 offline update method
\item .NET Framework 4.5.2 resolution 
\item Notes on NISPOM
\item 
\end{itemize}

\subsection{\date{4/14/2016}}
\begin{itemize} 
\item CentOS 5 offline update method
\item .NET Framework 4.5.2 resolution
\item Notes on NISPOM
\item DataCenter image update
\end{itemize}

\subsection{\date{4/15/2016}}
\begin{itemize} 
\item 10 DataCenter Zbooks
\item CATS Zbooks image
\item 
\item 
\end{itemize}

\subsection{\date{4/18/2016}}
\begin{itemize} 
\item CATS Zbook image
\item Resume and NDA for SAIC contract
\item JAT image update
\item 
\end{itemize}

\subsection{\date{4/19/2016}}
\begin{itemize} 
\item SQL permissions
\item JAT LAN AV update
\item CDS3 image update
\item System Admin training with security
\end{itemize}

\subsection{\date{4/20/2016}}
\begin{itemize} 
\item JATDev image update
\item CDS3 ubstor.sys error
\item Windows Installer error on PTS machines
\item 
\end{itemize}

\subsection{\date{4/21/2016}}
\begin{itemize} 
\item 3 DataCenter PCs
\item Audit Training in L2.
\item Cowboy image for L2. Removed Red Hat and VMWare
\item 
\end{itemize}

\subsection{\date{4/22/2016}}
\begin{itemize} 
\item JATLAN Linux AV
\item Imaged 5 L2 PCs with variant Cowboy image. 
\item 
\item 
\end{itemize}

\subsection{\date{4/25/2016}}
\begin{itemize} 
\item DataCenter PCs imaging
\item Garage door repair
\item Packing L2 for travel. 
\item 
\end{itemize}

\subsection{\date{4/26/2016}}
\begin{itemize} 
\item Cleaning labs for DSS.
\item Packing L2 for travel.
\item Trailer 4 support for Engineering meeting.
\item Notes on NISPOM
\end{itemize}

\subsection{\date{4/27/2016}}
\begin{itemize} 
\item 5 DataCenter PCs
\item 3 CDS3 PCs
\item Update 2 CDS3 PCs
\item Delete video files
\end{itemize}

\subsection{\date{4/28/2016}}
\begin{itemize} 
\item Load truck for YPG
\item Z840 update and imaging
\item 
\item 
\end{itemize}

\subsection{\date{4/29/2016}}
\begin{itemize} 
\item 
\item Out of office. 
\item 
\item 
\end{itemize}
\end{multicols}